---
title: "Developing data products pitch"
subtitle: "Predicting the price of a diamond based on its carat size"
author: "Bruno Hoste"
date: "2-9-2020"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

This is the pitch for the final peer graded assignment in the Developing Data Products class.

The goal of our little shiny app is to determine the price of a diamond based on its carat size.

The app can be found on following link:
http://brunohoste.shinyapps.io/Assignment/

The code (UI.R and server.R) can be found on github:
http://github.com/BrunoHoste/developing-data-products

## Method

We started with the diamond dataset from the UsingR package. It has observations for carat size and price of 48 diamonds. 
```{r,echo=TRUE,eval=TRUE,warning=FALSE,message=FALSE}
library(UsingR)
data("diamond")
dim(diamond)
head(diamond)
```

We did a simple linear regression on that dataset to make our predictions. 


## Regression

The outcome of the regression model used for our predictions turns out to be quite satisfying: significant coefficients and an R-squared of almost 98%.

```{r, echo = TRUE, eval=TRUE}
model <- lm(price~carat,data=diamond)
summary(model)
```

## Predictions

We therefore decided to use the model to make the predictions in our little shiny app. In the app, we also added
a plot and regression line. 

```{r, eval=TRUE,echo=TRUE}
plot(diamond$carat,diamond$price,xlab = "Carat size",
                     ylab = "Diamond price (in USD)")
                abline(model,col='red',lwd=2)
```

